Import OLIS spectral data

### 2023-12-04 Code/OlisImportPurCalc.Rmd
Copied OlisImportCombinedFiles.Rmd This rmd assigns CultureID to columns of Olis .asc files that were combinedinto 1 file. This file does not have a header.
Added chunk names

RdsData <-  OlisRdsFiles %>%
    map_df(~readRDS_plus(Flnm = .)) %>% 
  select(-c(...44,...45))

@@

Find Strain specific average PUR for each spectral color and each growth PAR 
```{r}

@@

write_csv(PicoNestedPurOlisData, file = file.path(DataOut, paste(Project, "NestedPurOlisData",".csv",sep = ""),fsep = .Platform$file.sep))

@@

AbsAllStrains
```

>>>>

RdsData <-  OlisRdsFiles %>%
    map_df(~readRDS_plus(Flnm = .))

@@

Find Strain specific average PUR for each spectral color and each growth PAR 
```{r Calc mean PUR}

@@

# write_csv(PicoNestedPurOlisData, file = file.path(DataOut, paste(Project, "NestedPurOlisData",".csv",sep = ""),fsep = .Platform$file.sep))

@@
